Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 Experiments.tex
scattered fixes in Section V.

We observe that, despite some fluctuations due to external factors (e.g.,
Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP ranges between 4500 and 4800 seconds. We
also observe that in all the cases the gap between AthenaMP execution times
and the pilot durations is minimal, although it slightly increases with the
pilot size. We notice that NGE's overhead does grow linearly with the number
of units.

\subsubsection{Weak scalability with multiple generation }

The NGE provides an important new capability of submitting multiple
generations of AthenaMP to the same pilot. In order to investigate the cost
of doing so, we performed a variant of the weak scalability experiments. This
stresses the pilot's components, as new tasks are scheduled for execution on
the Agent while other tasks are still running.

In these experiments, we run five AthenaMP instances per node. As these
experiments are designed to investigate the overhead of 
scheduling and bootstraping of AthenaMP instances, the number of
events simulated by each AthenaMP task was reduced to sixteen such that the
running time of each AthenaMP was, on average, $\sim 1200$ seconds. This
experiment design choice does not affect the objectives or accuracy of the
experiments, but allows us to scale experiments to large node counts by being
conservative with allocation.

@@

\begin{figure}[!t]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
        \vspace{-0.3in}
    \caption{Weak scalability with multiple generations: average pilot
    duration, average duration of sequential AthenaMP executions, and
    pilot's overhead for pilot with 256, 512, 1024 and 2048 nodes.}
\label{fig:weakScal2a}
\end{figure}

>>>>

We observe that, despite some fluctuations due to external factors (e.g.,
Titan's shared filesystem and the shared database used by the NGE), the
average execution time of AthenaMP ranges between 4500 and 4800 seconds. We
also observe that in all the cases the gap between AthenaMP execution times
and the pilot durations is minimal, although it slightly increases with the
pilot size. We notice that NGE's overhead grows linearly with the number
of units.

\subsubsection{Weak scalability with multiple generation}

The NGE provides an important new capability of submitting multiple
generations of tasks to the same pilot. In order to investigate the cost
of doing so, we performed a variant of the weak scalability experiments. This
stresses the pilot's components, as new tasks are scheduled for execution on
the Agent while other tasks are still running.

In these experiments, we run five AthenaMP instances per node. As these
experiments are designed to investigate the overhead of  scheduling and
bootstraping of AthenaMP instances, the number of events simulated by each
AthenaMP task was reduced to sixteen such that the running time of each
AthenaMP was $\sim 1200$ seconds on average. This experiment design choice
does not affect the objectives or accuracy of the experiments, but allows us
to scale experiments to large node counts by conserving project allocation.

@@

\begin{figure}[!t]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
        \vspace{-0.3in}
    \caption{Weak scalability with multiple generations (where each generation has approximately 1/6th the number of events compared to Fig. 7): average pilot
    duration, average duration of sequential AthenaMP executions, and
    pilot's overhead for pilot with 256, 512, 1024 and 2048 nodes.}
\label{fig:weakScal2a}
\end{figure}

### 2017-07-04 nge.tex
scattered fixes in Section V.

Multiple generations would also relax two assumptions of the current
execution model: knowing the number of simulations before submitting the MPI
script, and having a fixed number of events per simulation (100 at the
moment). Pilots would enable the scheduling of simulations independently from
whether they were available at the moment of submitting the pilot. Further,
simulations with a varying number of events could be scheduled on a pilot,
depending on the amount of remaining walltime and the distribution of
execution time per event, as shown in \S\ref{ssec:panda_titan},
Fig.~\ref{fig:comparison-8-16cores}. These capabilities would increase the
efficiency of the PanDA Broker when there is a large difference between the
number of cores and walltime.

>>>>

Multiple generations would also relax two assumptions of the current execution
model: knowing the number of simulations before submitting the MPI script, and
having a fixed number of events per simulation (currently 100). Pilots would
enable the scheduling of simulations independently from whether they were
available at the moment of submitting the pilot. Further, simulations with a
varying number of events could be scheduled on a pilot, depending on the
amount of remaining walltime and the distribution of execution time per event,
as shown in \S\ref{ssec:panda_titan}, Fig.~\ref{fig:comparison-8-16cores}.
These capabilities would increase the efficiency of the PanDA Broker when
there is a large difference between the number of cores and walltime.
